%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

    \cventry
    {Senior Software Engineer - Full-time} % Job title
    {Hellofresh} % Organization
    {Berlin, Germany} % Location
    {Feb. 2022 - Now} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Formulated and enhanced compensation algorithms to maximize efficiency and performance of Golang-based services.}
            \item {Engineered and deployed A/B testing frameworks to refine product features through systematic experimentation.}
            \item {Augmented GDPR compliance for internal tooling by automating account removal workflows, coinciding with the migration from legacy systems to modern platforms.}
            \item {Orchestrated and swiftly carried out the transition from RabbitMQ to Kafka, ensuring seamless integration and modernization of existing legacy systems.}
        \end{cvitems}
    }

%------------------------------------------------

    \cventry
    {Relocation}
    {Career Break}
    {Iran -> Germany}
    {Dec 2021 - Feb 2022 . 3 mos}
    {}

%------------------------------------------------

    \cventry
    {Senior Software Engineer - Full-time}
    {Cafebazaar}
    {Mashhad, Iran}
    {Aug. 2020 - Dec. 2021 . 1 yr 5 mos}
    {
        \begin{cvitems}
            \item { Improved microservices resource usage by 80\% by refactoring legacy code.}
            \item { Implemented message queues to exchange data between microservices, improving performance 3x.}
            \item { Minimized response times from 2 secs to 200ms using multi-level caching.}
            \item { Collaborated with a 10-person engineering team to maintain, develop and monitor high scale microservices and distributed systems handling millions of requests per day.}
            \item { Design, organize, and implement the integration with Archive-Patcher to cut down the size of update downloads, leading to a reduction of up to 70\% in download size.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer - Full-time}
    {EcollegeMe}
    {Mashhad, Iran}
    {Sep 2018 - Jul 2020 . 1 yr 11 mos}
    {
        \begin{cvitems}
            \item { Developed a microservice to handle user authentication and authorization, reducing the response time by 50\%.}
            \item { Implemented a new feature to allow users to upload and share their files, increasing user engagement by 30\%.}
            \item { Designed and implemented a new feature to allow users to create and manage their own courses, increasing user retention by 20\%.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer - Full-time}
    {IDS}
    {Mashhad, Iran}
    {Jan 2016 - Jun 2019. 3 yr 6 mos}
    {
        \begin{cvitems}
            \item { Developed and maintained server-side PHP applications.}
            \item { Contributed back-end experience and collaborated on APIs.}
            \item { Built reusable code that could be utilized in other projects, effectively saving the company money.}
        \end{cvitems}
    }
    \cventry
    {Software Engineer - Internship}
    {IDS}
    {Mashhad, Iran}
    {May 2015 - Dec 2015. 8 mos}
    {}
\end{cventries}